Title here

### 2017-05-05 portfolio/text/anderson-etal-rev-pfx.tex
Start revising paper

Our models focused on species diversity as a possible predictor of revenue and
revenue variability while controlling for effort. For consistency with previous
analyses \cite{vedeld2007, illukpitiya2008, debela2012, kasperski2013, sethi2014, cline2017}, we calculated effective species diversity
for permit holder \(i\) and time (year) \(t\) as the inverse of Simpson's
diversity index \(\lambda\) \cite{simpson1949, jost2006} (also referred to in
economics as the Herfindahl-Hirschman Index (HHI) \cite{hirschman1964}) weighted by
revenue \(R\):

>>>>

Our models focused on species diversity as a possible predictor of revenue and
revenue variability while controlling for effort. For consistency with previous
analyses \cite{vedeld2007, illukpitiya2008, debela2012, kasperski2013, sethi2014, cline2017}, we calculated effective species diversity
for permit holder \(i\) and time (year) \(t\) as the inverse of Simpson's
concentration index \(\lambda\) \cite{simpson1949, jost2006} (this index is also referred to in
economics as the Herfindahl-Hirschman Index (HHI) \cite{hirschman1964}) weighted by
revenue \(R\):

### 2017-05-05 portfolio/text/ms.Rmd
Start revising paper

Individual revenue variability decreases exponentially with higher mean fished
species diversity across combinations of state and federal fishing permits
("strategies"; Fig. \ref{fig:across}). Controlling for effort, strategies with
one unit higher mean species diversity had on average `r h1[[2]]`% (`r
h1[[1]]`--`r h1[[3]]`% 95% CI) lower variability. This pattern is
qualitatively similar with or without individuals targeting salmon. As examples,
revenue variability was highest for the herring roe gillnet and king crab fisheries.
Most strategies with the lowest estimated revenue variability combined halibut
with a salmon permit and had high levels of fished species diversity (Fig.
\ref{fig:across}).

@@

\caption{Diversifying permits reduces risk and usually increases revenue. Two
examples of expected revenue variability and median revenue for owners of (A)
individual halibut and (B) gillnet herring roe permits (dark blue) compared with
owners of the same permit plus one more (medium blue) or two more (light
blue) permits. On the y-axis, dots and lines represent posterior median and 95\%
credible intervals of expected standard deviations of year-to-year revenue rates
of return.}

@@

We also found that, within strategies, altering species diversity tended to be
associated with increased revenue variability. There are number of possible
reasons for this relationship. For instance, local knowledge and experience are
a major determinant of fishing efficiency [@hilborn1985a]. Therefore, changes to
fishing patterns may sometimes be associated with a learning or adaptation phase
as individuals become accustomed to new locations, gear, or species.
For example, many individuals fishing herring in Alaska in the 1970s 
<!-- AB: I think in this paragraph it would be good to pick an example or two and speculate on potential reasons specific to those permit strategies. Otherwise, statements like this one aren’t really anchored to anything concrete.  For example, what does increased specialization look like in the Hal ll permit, which showed one of the greatest effects of specialization on revenue diversity? How many permits could a Hal ll permit holder potentially fish? This goes back to my comment re: Table 1 (see p. 15) 
sea cuc - H W book - learning...
herring - alaska 1970s - learn to fish for roe ... [ref]
salmon - hatchery production - change target from diverse to most abundant... PWS seine - pink salmon or SE
Hal ll + S troll...
-->
Additionally, changes in diversity might reflect years in which targeted species
were less available and fishers instead chose to target other species or landed
more non-target species,
adding stochasticity to their revenue. Most importantly, this
increased variability reflects an inability for our model to predict
an individual's revenue in a subsequent year. There are many reasons, often
unique to an individual permit holder's behavior [@hilborn1985; @hilborn1985a;
@branch2006] and therefore not in our model, that might
make a specific individual's revenue less predictable if species diversity
changes.

>>>>

Individual revenue variability decreases exponentially with higher mean fished
species diversity across combinations of state and federal fishing permits
("strategies"; Fig. \ref{fig:across}). This pattern is
qualitatively similar with or without individuals targeting salmon. Controlling for effort, strategies with
one unit higher mean species diversity had on average `r h1[[2]]`% (`r
h1[[1]]`--`r h1[[3]]`% 95% CI) lower variability. As examples,
revenue variability was highest for the herring roe gillnet and king crab fisheries.
Most strategies with the lowest estimated revenue variability combined halibut
with a salmon permit and had high levels of fished species diversity (Fig.
\ref{fig:across}).

@@

\caption{Diversifying permits reduces risk and usually increases revenue. Two
examples of expected revenue variability and median revenue for owners of (A)
individual halibut and (B) gillnet herring roe permits (dark blue) compared with
owners of the same permit plus one more (medium blue) or two more (light
blue) permits. On the y-axis, dots and lines represent posterior median and 95\%
credible intervals of expected standard deviations of year-to-year revenue rates
of return. Angled lines connects permit sets that differ by one permit.}

@@

We also found that, within strategies, altering species diversity tended to be
associated with increased revenue variability. There are number of possible
reasons for this relationship. For instance, local knowledge and experience are
a major determinant of fishing efficiency [@hilborn1985a]. Therefore, changes to
fishing patterns may sometimes be associated with a learning or adaptation phase
as individuals become accustomed to new locations, gear, or species.
<!-- For example, many individuals fishing herring in Alaska in the 1970s --> 
<!-- AB: I think in this paragraph it would be good to pick an example or two and speculate on potential reasons specific to those permit strategies. Otherwise, statements like this one aren’t really anchored to anything concrete.  For example, what does increased specialization look like in the Hal ll permit, which showed one of the greatest effects of specialization on revenue diversity? How many permits could a Hal ll permit holder potentially fish? This goes back to my comment re: Table 1 (see p. 15) 
sea cuc - H W book - learning...
herring - alaska 1970s - learn to fish for roe ... [ref]
salmon - hatchery production - change target from diverse to most abundant... PWS seine - pink salmon or SE
Hal ll + S troll...
-->
Additionally, changes in diversity might reflect years in which targeted species
were less available and fishers instead chose to target other species or landed
more non-target species,
adding stochasticity to their revenue. Most importantly, this
increased variability reflects an inability for our model to predict
an individual's revenue in a subsequent year. There are many reasons, often
unique to an individual permit holder's behavior [@hilborn1985; @hilborn1985a;
@branch2006] and therefore not in our model, that might
make a specific individual's revenue less predictable if species diversity
changes.
